SST_patterns

### 2019-10-26 SST_patterns.Rmd
Error CMC

```{r}
library(ggpubr)
year_func <- function(df){
  Filtered <- df %>%
filter(year(date_start) %in% seq(2010, 2014, 1))
}

@@

plot_scat_func <- function(df){
  ggplot(data = df, aes(x = date_start, y = intensity_mean)) +
  geom_point() +
  scale_x_date(expand = c(0, 0)) +
  facet_wrap(~distance, ncol = 2) +
  theme_grey() +
  labs(y = "Mean Intensity", x = NULL)
}
(CMC_SP_plot <- plot_scat_func(df = CMC_SEAPOINT))
(CMC_SB_plot <- plot_scat_func(df = CMC_SB))
(CMC_PN_plot <- plot_scat_func(df = CMC_PN))
(CMC_LB_plot <- plot_scat_func(df = CMC_LB))

CMC_SP_plot <- CMC_SP_plot +
  ggtitle("Sea Point") 
CMC_SB_plot <- CMC_SB_plot +
  ggtitle("Saldanha Bay")
CMC_PN_plot <- CMC_PN_plot +
  ggtitle("Port Nolloth")
CMC_LB_plot <- CMC_LB_plot +
  ggtitle("Lamberts Bay")

combined_CMC <- ggarrange(CMC_SP_plot, CMC_SB_plot, CMC_PN_plot,CMC_LB_plot)
###################
## OISST
OISST_SEAPOINT <- OISST_filtered %>% 
  filter(site == "Sea Point")
OISST_SB <- OISST_filtered %>% 
  filter(site == "Saldanha Bay")
OISST_PN <- OISST_filtered %>% 
  filter(site == "Port Nolloth")
OISST_LB <- OISST_filtered %>% 
  filter(site == "Lamberts Bay")

plot_scat_func <- function(df){
  ggplot(data = df, aes(x = date_start, y = intensity_mean)) +
  geom_point() +
  scale_x_date(expand = c(0, 0)) +
  facet_wrap(~distance, ncol = 2) +
  theme_grey() +
  labs(y = "Mean Intensity", x = NULL)
}
(OISST_SP_plot <- plot_scat_func(df = OISST_SEAPOINT))
(OISST_SB_plot <- plot_scat_func(df = OISST_SB))
(OISST_PN_plot <- plot_scat_func(df = OISST_PN))
(OISST_LB_plot <- plot_scat_func(df = OISST_LB))

OISST_SP_plot <- OISST_SP_plot +
  ggtitle("Sea Point")
OISST_SB_plot <- OISST_SB_plot +
  ggtitle("Saldanha Bay")
OISST_PN_plot <- OISST_PN_plot +
  ggtitle("Port Nolloth")
OISST_LB_plot <- OISST_LB_plot +
  ggtitle("Lamberts Bay")

combined_OISST <- ggarrange(OISST_SP_plot, OISST_SB_plot, OISST_PN_plot,OISST_LB_plot)

############## 
# SACTN

plot_scat_func <- function(df){
  ggplot(data = df, aes(x = date_start, y = intensity_mean)) +
  geom_point() +
  scale_x_date(expand = c(0, 0)) +
  facet_wrap(~site, ncol = 2) +
  theme_grey() +
  labs(y = "Mean Intensity", x = NULL)
}
(SACTN_plot <- plot_scat_func(df = SACTN_filtered))

@@

```{r}
plot_loli_func <- function(df){
  ggplot(df, aes(x = date_peak, y = duration)) + 
  geom_lolli(colour = "steelblue3", colour_n = "navy", n = 3) + 
  #scale_color_distiller(palette = "Spectral", name = "Cumulative \nintensity") + 
  facet_wrap(~distance, ncol = 2) +
  scale_y_continuous(breaks = c(5,10,15,20,25,30),
                     limits = c(1,30)) +
  theme_bw() +
  theme(axis.text=element_text(size=17),
        axis.title=element_text(size=17)) +
  theme(strip.text.x = element_text(size = 17))+
  theme(panel.spacing = unit(0.5, "lines")) +
  #strip=strip.custom(var.name=c("10km", "20km", "30km", "40km", "50km")) +
  xlab("Date (years)") + ylab("Event duration (days)") 
}

>>>>

load("Data/OISST_upwell_base.RData")
load("Data/CMC_upwell_base.RData")
load("Data/SACTN_upwell_base.RData")

library(ggpubr)
year_func <- function(df){
  Filtered <- df %>%
filter(year(date_start) %in% seq(2011, 2013, 1))
}

@@

###################
## OISST
OISST_SEAPOINT <- OISST_filtered %>% 
  filter(site == "Sea Point")
OISST_SB <- OISST_filtered %>% 
  filter(site == "Saldanha Bay")
OISST_PN <- OISST_filtered %>% 
  filter(site == "Port Nolloth")
OISST_LB <- OISST_filtered %>% 
  filter(site == "Lamberts Bay")

@@

```{r}
plot_loli_func <- function(df){
  ggplot(df, aes(x = date_peak, y = duration)) + 
  geom_lolli(colour = "steelblue3", colour_n = "navy", n = 3) + 
  #scale_color_distiller(palette = "Spectral", name = "Cumulative \nintensity") + 
  facet_wrap(~distance, ncol = 2) +
  scale_y_continuous(breaks = c(5,10,15,20,25,30),
                     limits = c(1,30)) +
  theme_bw() +
  theme(axis.text=element_text(size=15),
        axis.title=element_text(size=17)) +
  theme(strip.text.x = element_text(size = 17))+
  theme(panel.spacing = unit(1, "lines")) +
  #strip=strip.custom(var.name=c("10km", "20km", "30km", "40km", "50km")) +
  xlab("Date (years)") + ylab("Event duration (days)") 
}
